Neural Networks for Neural Tumors\\ \vspace{-0.6em} {\footnotesize Final Project for \textit{ECS 171 - Machine Learning} at UC Davis, with Professor Setareh Rafatirad}

### 2025-06-06 latex/draft.tex
added support column back to metric tables
Add Nam's contributions

\begin{table}[h!]
\centering
\caption{CNN Metrics}
\begin{tabular}{lccc}
\toprule
\textbf{Class} & \textbf{Precision} & \textbf{Recall} & \textbf{F1-score} \\
\midrule
glioma     & 0.98 & 0.93 & 0.95 \\
meningioma & 0.93 & 0.97 & 0.95 \\
no tumor   & 0.97 & 0.98 & 0.98 \\
pituitary  & 0.99 & 0.99 & 0.99 \\
\midrule
\textbf{Accuracy} \textbf{0.97} \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[h!]
\centering
\caption{SVM Metrics}
\begin{tabular}{lccc}
\toprule
\textbf{Class} & \textbf{Precision} & \textbf{Recall} & \textbf{F1-score} \\
\midrule
glioma     & 0.98 & 0.91 & 0.94 \\
meningioma & 0.89 & 0.97 & 0.93 \\
no tumor   & 0.98 & 0.97 & 0.97 \\
pituitary  & 0.98 & 0.98 & 0.98 \\
\midrule
\textbf{Accuracy} \textbf{0.96} \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{RF Metrics}
\begin{tabular}{lccc}
\toprule
\textbf{Class} & \textbf{Precision} & \textbf{Recall} & \textbf{F1-score} \\
\midrule
glioma     & 0.98 & 0.89 & 0.93 \\
meningioma & 0.87 & 0.98 & 0.92 \\
no tumor   & 1.00 & 0.93 & 0.97 \\
pituitary  & 0.97 & 0.98 & 0.98 \\
\midrule
\textbf{Accuracy} \textbf{0.95} \\
\bottomrule
\end{tabular}
\end{table}

@@

Nam: Nam took charge of making the first prototype of our model. Having this model as a starting and reference point is absolutely crucial in the development of subsequent models. In the next few weeks, Nam will be researching different frameworks and libraries to develop other CNN models to see which best fit our dataset.

>>>>

\begin{table}[h!]
\centering
\caption{CNN Metrics}
\begin{tabular}{lcccc}
\toprule
\textbf{Class} & \textbf{Precision} & \textbf{Recall} & \textbf{F1-score} & \textbf{Support} \\
\midrule
glioma     & 0.98 & 0.93 & 0.95 & 109 \\
meningioma & 0.93 & 0.97 & 0.95 & 105 \\
no tumor   & 0.97 & 0.98 & 0.98 & 60 \\
pituitary  & 0.99 & 0.99 & 0.99 & 118 \\
\midrule
\textbf{Accuracy} \textbf{0.97} \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[h!]
\centering
\caption{SVM Metrics}
\begin{tabular}{lcccc}
\toprule
\textbf{Class} & \textbf{Precision} & \textbf{Recall} & \textbf{F1-score} & \textbf{Support} \\
\midrule
glioma     & 0.98 & 0.91 & 0.94 & 109 \\
meningioma & 0.89 & 0.97 & 0.93 & 105 \\
no tumor   & 0.98 & 0.97 & 0.97 & 60 \\
pituitary  & 0.98 & 0.98 & 0.98 & 118 \\
\midrule
\textbf{Accuracy} \textbf{0.96} \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{RF Metrics}
\begin{tabular}{lcccc}
\toprule
\textbf{Class} & \textbf{Precision} & \textbf{Recall} & \textbf{F1-score} & \textbf{Support} \\
\midrule
glioma     & 0.98 & 0.89 & 0.93 & 109 \\
meningioma & 0.87 & 0.98 & 0.92 & 105 \\
no tumor   & 1.00 & 0.93 & 0.97 & 60 \\
pituitary  & 0.97 & 0.98 & 0.98 & 118 \\
\midrule
\textbf{Accuracy} \textbf{0.95} \\
\bottomrule
\end{tabular}
\end{table}

@@

Nam: Throughout the progression of the project, Nam was primarily responsible for the development and implementation of machine learning models. 
Nam took over the experimental process to optimize each model, iteratively researching multiple architectures and frameworks to successfully develop models with different algorithms that are able to perform brain tumor detection at a relatively high accuracy. 
In general, Nam’s contributions encompassed every stage of model development, from initial prototyping to completion of each model prior to final deployment, ensuring both technical robustness and adaptability to team-driven refinements.
